`r params$title`

### 2019-09-13 Rmd/summary_db_cols_norman.Rmd
changes

```{r params, echo=FALSE, include=FALSE}
schema = params$schema
table = params$table
cols = params$cols
dir = file.path(params$output_dir, paste0(schema, '_', table))
# debuging
# schema = 'norman'
# table = 'data1'
# cols = c('nor3', 'nor4')
```

@@

```{r echo=FALSE, message=FALSE}
# schema = 'norman'
# table = 'data2_newest'
# cols = c('nor85', 'nor88')

## table
tab = summary_db_all(schema = schema, table = table)
## cols
l = summary_db_cols(schema = schema, table = table, cols = cols)
## names lookup table
q = "SELECT *
     FROM norman.variables"
var = read_tbl(user = DBuser, host = DBhost, port = DBport, password = DBpassword, dbname = DBetox,
               query = q)
```

@@

  dat = l[[col]]
  dat[ , var20 := substr(get(col), 1, 20) ]
  header = var[ match(names(dat)[1], var$id), norman_header ]

@@

  message('Writing: ', fl)
  fwrite(dat, fl)
}
```

```{r write-single-file, message=FALSE}
# write summary to single file
dat = cbind_fill(dflist = l, limit = NULL)
names(dat)[ seq(1, length(names(dat)), 2) + 1 ] = paste0(names(dat)[ seq(1, length(names(dat)), 2) ], '_n')

>>>>

```{r params, echo=FALSE, include=FALSE}
schema = params$schema
table = params$table
cols = params$cols
dir = file.path(params$output_dir, paste0(schema, '_', table))
# debuging
# dir = '/tmp'
# schema = 'norman'
# table = 'data2_newest'
# cols = c('nor1', 'nor3', 'nor4', 'nor5', 'nor6')
```

@@

```{r echo=FALSE, message=FALSE}
## table
tab = summary_db_all(schema = schema, table = table)
## cols
l = summary_db_cols(schema = schema, table = table, cols = cols)
## names lookup table
q = "SELECT *
     FROM norman.variables"
var = read_tbl(user = DBuser, host = DBhost, port = DBport, password = DBpassword, dbname = DBetox,
               query = q)
```

@@

  dat = copy(l[[col]])
  dat[ , var20 := substr(get(col), 1, 20) ]
  header = var[ match(names(dat)[1], var$id), norman_header ]

@@

  message('Writing: ', fl)
  fwrite(dat, fl, sep = ';')
}
```

```{r write-single-file, message=FALSE}
# write summary to single file
dat = cbind_fill(dflist = l, limit = 5000)
# names(dat)[ seq(1, length(names(dat)), 2) + 1 ] = paste0(names(dat)[ seq(1, length(names(dat)), 2) ], '_n')
